---
title: "Assignment Task"
author: "Ryan Isaacs - 202001716"
date: "16/11/2020"
output: html_document
---

# 1. Basics


1.1)What is the value of " B " after running these command?  
B = 5.0 + 10/12 = 5.8333

What type of vector do you get in each of the following?  
```{r}
vec_1 <- c(44, 5, 0, "k")
vec_2 <- c(1, 2, 3, FALSE)
vec_3 <- c("a", "b", "c", TRUE)
vec_4 <- c(1, 2, 3, "4")
```

vec_1 is char   
vec_2 is num  
vec_3 is char  
vec_4 is char
  
  
1.2.1)Create a vector vec_1 with no missing values using conditional subsetting and explain your code  
This code will omit all values of NA inside vector c.
```{r, echo=TRUE, message=FALSE, warning=FALSE}
vec <- c(141.2741, 141.8392, 140.5730,NA, 141.3571, 139.8689, 
         137.9384, NA,139.6620, 138.2521, 138.8635, 141.3885, NA)

new_vec1 <- na.omit(vec)

```


1.2.2)Create a vector of indexes of missing values using conditional subsetting and explain your code  
vec_2 will check through all values in the vector and check whether there are missing values(NA). If so it will return their indexes  
```{r echo=TRUE, message=FALSE, warning=FALSE}

new_vec2 <- which(!complete.cases(vec))


```
  
1.2.3) Write a code to determine how many missing values are in vec.  
Code will change Values to true and NA to False then will sum all incomplete cases (false).
```{r, echo=TRUE, message=FALSE, warning=FALSE}

new_vec2 <- (!complete.cases(vec))  
amt <- sum(new_vec2)

```

  
1.2.4) Write a R code to create a data frame which contains details of 3 students  
```{r, echo=TRUE, message=FALSE, warning=FALSE}

n <- c("Ryan", "Jody", "Rory")  
s <- c("Isaacs", "Simons", "Isaacs")  
a <- c(18, 23, 53)  
g <- c("M","F", "M")  
  
Students <- data.frame(Name= n,
                 Surname= s,
                 Age= a,
                 Gender= g)

```


# 2. Functions in R  


2.1) Create a function which returns a mean of an input vector and explain your code  
This function will sum all values inside the vector and divide the total by the amount of values present in the vector
```{r, echo=TRUE, message=FALSE, warning=FALSE}

vector <- c(10,20,15,16) 
mean_ans <- mean(vector) 

```

 
2.2) Create a function which take no inputs , it reads a Titanic .csv file and returns its content and explain your code.  
```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)  
library(readxl)

readTitanic <- tibble(read.csv("Titanic.csv"))

```
  
  
# 3. Conditionals and Loops
  
3.1)Write a function that take an input below and returns a transformed vector below into 1 when its element is male and 2 when its female using ifelse
```{r echo=TRUE, message=FALSE, warning=FALSE}

g <- c("MALE","FEMALE","FEMALE","MALE","FEMALE","MALE","MALE","FEMALE", "MALE","MALE","FEMALE","MALE","MALE","FEMALE","MALE","MALE","MALE")

ifelse(g=="MALE",1,2)

#or

g <- c("MALE","FEMALE","FEMALE","MALE","FEMALE","MALE","MALE","FEMALE", "MALE","MALE","FEMALE","MALE","MALE","FEMALE","MALE","MALE","MALE")

a <-factor(g, levels = c("MALE","FEMALE"), labels = c(1,2))

```

    
3.2.1)Use the "cbind " function in R to create one dataset and assign it to df
```{r}
x <- rnorm(1000, 120, 5)
y <- sample(c("M","F"),size = 1000, replace = TRUE)

df <- cbind(x,y, deparse.level =1)

```
  
  
3.2.2)Convert df from 3.2.1 into a data.frame
```{r}

new_df <- data.frame(df)

```
  
  
3.2.3)Write a code using tidyverse to compute a number of males ("M") and females ("F") in 3.2.1
```{r}
library(tidyverse)
library(readxl)

Males <- new_df %>% filter(y== "M") %>% count()

Females <- new_df %>% filter(y== "F") %>% count()

both <- new_df %>% group_by(y) %>% count()


```
  
  
3.2.4)Create a bar plot using ggplot to visualize your results in 3.2.3
```{r}

library(ggplot2)

new_df %>% group_by(y) %>% count() %>% 
  ggplot(aes(x=n, y=y ,fill=y))+
    geom_col()+
  labs(x="Count", y = "Male or Female", title= "Number of Male/Female")+
  coord_flip()+
  geom_text(aes(label=n), position = position_stack(vjust=0.5))+
  theme(plot.title=element_text(hjust=0.5))+
  guides(fill=guide_legend(title = "Gender"))
```

3.2.5)Use mutate function to add sum of x per "M" and "F" and plot the results using sum of x per "M" and "F"
```{r}



Mdf <- new_df %>% mutate(Male = ifelse(y=="M",x,0)) %>% mutate(Female = ifelse(y=="F",x, 0))

FemaleTotal <- sum(as.integer(Mdf$Female))
MaleTotal <- sum(as.integer(Mdf$Male))


Genders <-c("Male", "Female")
totals <- c(MaleTotal,FemaleTotal)

GraphData <- data.frame(Gender=Genders,
                        Amouts=totals)

GraphData %>% 
  ggplot(aes(x=Genders,y=totals, fill= as.factor(totals)))+
    geom_col()+
  labs(x="Genders", y = "Amout in X", title= "Total X values for Male and Female")+
  theme(plot.title=element_text(hjust=0.5))+
  geom_text(aes(label=totals), position = position_stack(vjust=0.5))+
  guides(fill=guide_legend(title = "Key"))




```

