---
title: "Assignment Task"
author: "Ryan Isaacs - 202001716"
date: "16/11/2020"
output: html_document
---


# 1. Basics


1.1)    B = 5.0 + 10/12 = 5.8333  
vec_1 is char   
vec_2 is num  
vec_3 is char  
vec_4 is char
  
  
1.2.1)    This code will omit all values of NA inside vector c.
```{r, echo=TRUE, message=FALSE, warning=FALSE}
vec <- c(141.2741, 141.8392, 140.5730,NA, 141.3571, 139.8689, 
         137.9384, NA,139.6620, 138.2521, 138.8635, 141.3885, NA)

vec_1 <- na.omit(vec)

```


1.2.2) vec_2 will check through all values in the vector and check whether there are missing values(NA). If so it will return their indexes  
```{r echo=TRUE, message=FALSE, warning=FALSE}

vec_2 <- which(!complete.cases(vec))


```
  
1.2.3) Code will change Values to true and NA to False then will sum all incomplete cases (false).
```{r, echo=TRUE, message=FALSE, warning=FALSE}

vec_2 <- (!complete.cases(vec))  
amt <- sum(vec_2)

```

  
1.2.4) 
```{r, echo=TRUE, message=FALSE, warning=FALSE}

n <- c("Ryan", "Jody", "Rory")  
s <- c("Isaacs", "Simons", "Isaacs")  
a <- c(18, 23, 53)  
g <- c("M","F", "M")  
  
Students <- data.frame(Name= n,
                 Surname= s,
                 Age= a,
                 Gender= g)

```


# 2. Functions in R  


2.1) This function will sum all values inside the vector and divide the total by the amount of values present in the vector
```{r, echo=TRUE, message=FALSE, warning=FALSE}

vector <- c(10,20,15,16) 
Ans <-mean(vector) 

```

 
2.2) 
```{r, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)  
library(readxl)

readTitanic <- tibble(read.csv("Titanic.csv"))

```
  
  
# 3. Conditionals and Loops
  
3.1)
```{r echo=TRUE, message=FALSE, warning=FALSE}

g <- c("MALE","FEMALE","FEMALE","MALE","FEMALE","MALE","MALE","FEMALE", "MALE","MALE","FEMALE","MALE","MALE","FEMALE","MALE","MALE","MALE")  
  
  a <-factor(g, levels = c("MALE","FEMALE"), labels = c(1,2))

```

    
3.2.1)
```{r}
x <- rnorm(1000, 120, 5)
y <- sample(c("M","F"),size = 1000, replace = TRUE)

df <- cbind(x,y, deparse.level =1)

```
  
  
3.2.2)
```{r}

new_df <- data.frame(df)

```
  
  
3.2.3)
```{r}
library(tidyverse)
library(readxl)

Males <- new_df %>% filter(y== "M") %>% count()

Females <- new_df %>% filter(y== "F") %>% count()

both <- new_df %>% group_by(y) %>% count()


```
  
  
3.2.4)
```{r}

library(ggplot2)

new_df %>% group_by(y) %>% count() %>% 
  ggplot(aes(x=n, y=y ,fill=y))+
    geom_col()+
  labs(x="Count", y = "Male or Female", title= "Number of Male/Female")+
  coord_flip()+
  geom_text(aes(label=n), position = position_stack(vjust=0.5))+
  theme(plot.title=element_text(hjust=0.5))+
  guides(fill=guide_legend(title = "Gender"))

```

3.2.5)
```{r}

```

